### 2022-08-09 main/chapter_2ljets.tex
add a missing roofit backslack

Although I have found no \atlas\ search reporting a discovery region limit
below $3$, there are published examples with zero data but larger observed
limits~\cite{SUSY-2018-36, atlas_susy_strong_0l}.
The most extreme is $\mathrm{SR}3\ell_{[90,110]}$
of~\cite{SUSY-2018-36}, which reports a background expectation of
$1.08 \pm 0.18$ and expected limits of
$S_{\mathrm{exp}}^{95} = 3.8^{+1.3}_{-0.5}$, but zero observed data with a
whopping $S_{\mathrm{obs}}^{95} = 4.8$.
Using their \pyhf\ models published through \hepdata, I have failed to
reproduce this effect outside the \histfitter-\roofit system, finding instead
a limit close to $3$. It would not surprise me if similar complications with
the test statistic distribution played a part.

>>>>

Although I have found no \atlas\ search reporting a discovery region limit
below $3$, there are published examples with zero data but larger observed
limits~\cite{SUSY-2018-36, atlas_susy_strong_0l}.
The most extreme is $\mathrm{SR}3\ell_{[90,110]}$
of~\cite{SUSY-2018-36}, which reports a background expectation of
$1.08 \pm 0.18$ and expected limits of
$S_{\mathrm{exp}}^{95} = 3.8^{+1.3}_{-0.5}$, but zero observed data with a
whopping $S_{\mathrm{obs}}^{95} = 4.8$.
Using their \pyhf\ models published through \hepdata, I have failed to
reproduce this effect outside the \histfitter-\roofit\ system, finding instead
a limit close to $3$. It would not surprise me if similar complications with
the test statistic distribution played a part.
